---
title: "Lab 3"
author: "Drew Hoffman, Tanner Ball, Burke Parent, David Washburn, Brandon Nelsen"
date: "9/10/2019"
output: html_document
---

**Overall question:** 
What is the overall average difference in weight vs desired weight between men and women?

**Why does this matter:** 
We are looking at if the average desired weight between men and women is different this can help us answer questions about how each gender prefers their overall weight change. Furthermore, our findings could give insight into how American society shapes the different desires of weight between men and women, which could then lead to unique differences in factors like exercise and overall health.

```{r include = FALSE}
library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
```
```{r echo = FALSE}
ggplot(data = cdc, mapping = aes(x = weight, y = wtdesire, color = gender)) +
  geom_point() +
  geom_abline(aes(intercept = 0, slope = 1), data = cdc) +
  geom_smooth(method = 'lm', color = "black") +
  facet_wrap(~gender)
```
David's Graph
```{r}
ggplot(data = cdc, mapping = aes(x = age, y = wtdesire - weight, linetype = gender)) +
  geom_smooth(se = FALSE) +
  theme_classic()

### y calculates how much someone wanted to change their weight by, a negative value meant that they wanted to lose weight
```
Burke's Individual Graph:
```{r}
ggplot(data = cdc, mapping = aes(x = age, y = smoke100))
```
Tanner's Individual Graph:
```{r}
ggplot(data=cdc, mapping=aes(x = weight, y = wtdesire)) + geom_jitter(mapping=aes(color=gender))+geom_smooth(se=FALSE)+facet_wrap(~ exerany)

### a look into whether the weight vs desired weight is different among those who have exercised in the past month vs those who haven't.
```
**Drew's Individual Graph:**
A plot of those who have smoked 100 cigarettes in their lives versus those that haven't. They are categorized by general health. In the healthier categories, the rate of smoking is lower than in worse health categories. The rate is drastically lower among those with excellent health but there are still a significant amount of smokers at every other health category.
```{r}
ggplot(data = cdc) + geom_bar(mapping=aes(x = smoke100)) + facet_wrap(~ genhlth)
```

```{r echo = FALSE}
ggplot(data = cdc)+
  stat_bin(mapping = aes(x = height, color = gender), binwidth = 1)
```
```{r echo = FALSE}
ggplot(data = cdc)+
  stat_bin(mapping = aes(x = wtdesire, color = gender), binwidth = 11)
```


**Brandon's Individal Plots:** These two plots were created to show the similar trends in height and desired weight. One is a histogram of
height and the other is a histogram of desired weight, the two show similar trends to each other. The trend shows that height may prehaps affect the desired weight of an individual.



