---
title: "Lab 3"
author: "Drew Hoffman, Tanner Ball, Burke Parent, David Washburn, Brandon Nelsen"
date: "9/10/2019"
output: html_document
---

**Overall question:** 
What is the overall average difference in weight vs desired weight between men and women?

**Why does this matter:** 
We are looking at if the average desired weight between men and women is different this can help us answer questions about how each gender prefers their overall weight change. Furthermore, our findings could give insight into how American society shapes the different desires of weight between men and women, which could then lead to unique differences in factors like exercise and overall health.

```{r}
library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
```
```{r}
ggplot(data = cdc, mapping = aes(x = weight, y = wtdesire, color = gender)) +
  geom_point() +
  geom_abline(aes(intercept = 0, slope = 1), data = cdc) +
  geom_smooth(method = 'lm', color = "black") +
  facet_wrap(~gender)
```

